%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{{\LARGE Yashkumar Maheshwari}} \\
            \href{mailto:yash37m@gmail.com}{yash37m@asu.edu} $\vert$ { +1-(602) 884 6837} $\vert$ {Tempe, Arizona, United States}\\
		\href{https://www.linkedin.com/in/yash37m}{linkedin.com/in/yash37m} $\vert$ \href{https://github.com/yash37m}{github.com/yash37m} \\
	\end{tabular*}
	
	%-----------EDUCATION-----------------
	\vspace{2pt}
	
	
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
        {Master of Science - Computer Software Engineering}{Aug'22 - Present}
	{Arizona State University}{Tempe, Arizona, USA}
	{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Current GPA:} 3.89/4.0}      
        % {\newline{}\textbf{Scholarships:} New American University Scholar worth \$ 6,000/year}
        {\newline{}\textbf{Courses:} Foundation of software Engineering, Software Design, Advanced Data Structures and Algorithms, Data Visualisation,\newline{} Human Computer Interaction, Knowledge Representation and Reasoning, Software Verification-Validation and Testing,\newline{} Semantic Web Engineering, Paradigm of Programming Languages}}}
	
	\resumeSubheading
 {Bachelor of Engineering - Computer Engineering}{Jul '18 - May '22}
	{Gujarat Technological University}{Ahmedabad, Gujarat, India}
	
	{\scriptsize \textit{ \footnotesize{\newline{}\textbf{GPA:} 8.96/10.0}
    {\newline{}\textbf{Courses:} Data Structures and Algorithms, Operating Systems, Software Engineering, Database Management System, Artificial Intelligence, Computer Networks, Machine Learning, Data Mining}}}
		
	\resumeSubHeadingListEnd
	
	\vspace{3pt}
	
	
	\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{\hspace{0.5cm}Python, Java, C++, JavaScript}
	%\vspace{2pt}
	\resumeSubItem{Frameworks}{\hspace{0.2cm}SK Learn, TensorFlow, Keras, Django, Dialogflow, OSRM, Pandas, Matplotlib, Open CV, Spring}
	%\vspace{2pt}
	\resumeSubItem{Tools}{\hspace{1.3cm}GIT, AWS, MySQL, MongoDB, Celery, OR Tools, LaTeX}
	%\vspace{2pt}
	% \resumeSubItem{Platforms}{\hspace{0.6cm}Linux, Windows, MacOS}
	% %\vspace{2pt}
	\resumeSubItem{Soft Skills}{\hspace{0.56cm}Leadership, Collaborative Working, Event Management, Public Speaking, Time Management}
	
	\resumeSubHeadingListEnd
	\vspace{7pt}
	
	
	
	
		
	\section{Work Experience}
	\resumeSubHeadingListStart
	%\resumeSubheading
        %{Tolleson Elementary School Tutor}{Nov '22 - Present}
	%{Arizona State University}{Downtown Campus}
	%\resumeItemListStart
	%\resumeItem{Student Worker III}{Currently a Student Worker III at ASU and serving as an Elementary school tutor, tutoring kids in subjects of 
	%mathematics and english.}
	%\resumeItem{Mentoring their progress}{Mentoring students so that they can cope up with physical studies especially after COVID-19 and ensuring their mental health}
	%\resumeItem{Collaborating with Teachers}{Worked together with teachers and staff to bridge any gaps in education and ensured that students are doing well in the class}
	%\resumeItem{Assisting in Managerial duties}{Performed any necessary managerial duties required for smooth functioning of schools}
	%\resumeItemListEnd
	\resumeSubheading
        {Software Development Intern (AI/ML)}{Jan '22 - Jul '22}
        {Fero.Ai}{Ahmedabad, India}
	\resumeItemListStart
        \resumeItem {Responsibility}{Work with Intelligent Virtual Assistant (IVA) Team and added functionalities to existing product, build chat-bots for Logistics and Supply Chain Industry with Dialogflow NLU Engine and Django as backend}
	\resumeItem{Prototype Tool}{Integrated Dialogflow with Django to the presentation tool allowing to create dynamic conversation without explicit typing, saving time for developers to understand the product by 30\%.}
	\resumeItem{Route Optimization:}{Pre-processed data worth 80k instances, and created models to replace existing static route optimization service with in house ML enabled tool cutting companies cost to 50\%.}
	\resumeItemListEnd
	\resumeSubheading
        {Data Science and Business Analyst Intern}{Jul '21 -  Aug '21}
	{The Sparks Foundation}{Remote}
	\resumeItemListStart
	\resumeItem{Learning}
	{Worked and understood basic Machine Learning Algorithms and implementation}
        \resumeItem{Exploratory Data Analysis}{Performed EDA on 10K instances and create visualizations for sales of a superstore.}
	\resumeItem{Stock Prices Variation from News Headlines}
	{Used Time series Analysis to predict the changes in the stock prices based on the nature of the headlines on that day, where positive headlines caused stock to rise and negative to drop.}
	\resumeItemListEnd
 %        \resumeSubheading
 %            {Web Development Intern}{May '21 - Jun '21}
 %            {Creart Solution}{Remote}
	% \begin{itemize}
	% 	\item\small Developed an admin panel and provided CRUD operations for a ceramic company website using PHP backend, Laravel and MySQL database and 
 %            built a project management Web Application with Laravel containing features such as task management, tracking and assignment.
	% 	%\vspace{-2pt}
	% 	% \item\small Built a project management Web Application with Laravel containing features such as task management, tracking and assignment.
	% 	% \vspace{-2pt}
	% \end{itemize}
 
    \resumeSubheading
        {Software Development Intern}{Apr '21 -  Jul '21}
	{Dhanvantri Covid Hospital -  Government of India}{Ahmedabad, India}
	\resumeItemListStart
	\resumeItem{Data Processing}
	{Processed data stored in PostgreSQL on patient details, to make it usable for visualizations.}
        \resumeItem{Data Visualizations}{Created Bar Charts, Line graphs and Pie Charts for press release to visualize Patients admitted, Patient Recovery, Patients Discharged (Normal, DAMA), Death. with average 800 patients on premise daily.}
	\resumeItem{Dashboard Development}
	{Developed a complete dashboard with features like timeline and data scrolling, providing an interactive interface for users.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------------
	\vspace{7pt}
	\section{Projects}
	\resumeSubHeadingListStart
 
        \resumeSubItem{Safe-Screen : Non Invasive Child Monitoring app}
        \resumeItemListStart
        \resumeItem{Created REST APIs}{Developed REST APIs using Java to fetch data from different sources.}
        \resumeItem{Optimized data storage}{Optimized data storage using PostgreSQL, reducing data fetching times by 17\%.}
        \resumeItem{Data pipeline}{Created a data pipeline for sending and processing data to perform different functions.}
        \resumeItemListEnd
        
 
	\resumeSubItem{Automatic License Plate Recognition System}
        \newline{}
        \vspace{3pt}
	Automated the process of detecting the license plate using just a photo of vehicle. Optimized the detection time to enable real-time detection and applications. Implemented it using image segmentation and image processing using Keras.
        
        % \resumeSubItem{Resume Screener}
        % \newline{}
        % \vspace{3pt}
        % Used Natural Language Processing to automate the task of sorting resumes. Using models like LSTMs and Recurrent Neural Networks, implemented multiclass classification task so that it can be divided according to the applied role of the applicant.
        
        \resumeSubItem{Movie recommendation system}
        \newline{}
        \vspace{3pt}
        Built a movie recommendation system that takes into account the previously watched movies and suggests accordingly. Added the feature to filter out the suggested movies to further improve the recommendation system.

         \resumeSubItem{Multi-Lingual Voice Assistant}
        \newline{}
        \vspace{3pt}
        Built a Dialogflow based voice assistant with Django and used Google Translate API to satisfy the translation and enable language switching in between conversations. Used Redis to reduce the average response time by 50\% i.e. from 6 sec to 3 sec.
        
	 \resumeSubItem{Sudoku Solver / Challenger}
        \newline{}
        \vspace{3pt}
        Solve a Sudoku, verify your Solution to a Sudoku and allows to create a Sudoku board to challenge someone else.
	
	\vspace{7pt}
		
		\resumeSubHeadingListEnd
		
	\end{document}